---
title: "introduction"
author: "Bolong Zheng"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(binomial)
```

#Binomial Package
The package implements functions for calculating probabilities of a Binomial random variable, and related calculations such as the probability distribution, the expected value, variance, etc.

#combination
'bin_choose()' calculates the number of combinations in which k successes can occur in n trials.
```{r}
bin_choose(n = 5, k = 2)
bin_choose(5, 0)
bin_choose(5, 1:3)
```

#binomial probability
'bin_probability()' calculates the binomial probability in which k successes can occur in n trials where the probability for an individual trial to succeed is p.
```{r}
# 55 heads in 100 tosses of a loaded coin with 45% chance of heads
bin_probability(success = 55, trials = 100, prob = 0.45)
# probability of getting 2 successes in 5 trials
# (assuming prob of success = 0.5)
bin_probability(success = 2, trials = 5, prob = 0.5)
# probabilities of getting 2 or less successes in 5 trials
# (assuming prob of success = 0.5)
bin_probability(success = 0:2, trials = 5, prob = 0.5)
```

#binomial distribution
'bin_distribution()' creates a data frame for the binomial distribution.
```{r}
# binomial probability distribution
bin_distribution(trials = 5, prob = 0.5)
```
The plot function will present a nice visualization of a given binomial distribution
```{r, fig.show='hold'}
# plotting binomial probability distribution
dis1 <- bin_distribution(trials = 5, prob = 0.5)
plot(dis1)
```

#binomial cumulative distribution
Just like 'bin_distribution()', 'bin_cumulative()' creates a data frame and allows you to plot and visualize distribution. But the distribution and probability here is cumulative.
```{r}
# plotting binomial cumulative distribution
dis2 <- bin_cumulative(trials = 5, prob = 0.5)
plot(dis2)
```

#binomial variable
'bin_variable()' creates a binomial variable, which you can apply 'print', 'summary' to obtain statistical information about a binomial variable.
```{r}
bin1 <- bin_variable(trials = 10, p = 0.3)
bin1
```

```{r}
bin1 <- bin_variable(trials = 10, p = 0.3)
binsum1 <- summary(bin1)
binsum1
```

#functions of measures
Of course, this package also contains some basic and handy functions for statistical measures such as 'bin_mean()', 'bin_variance()','bin_mode()','bin_skewness()','bin_kurtosis()'
```{r}
bin_mean(10, 0.3)
bin_variance(10, 0.3)
bin_mode(10, 0.3)
bin_skewness(10, 0.3)
bin_kurtosis(10, 0.3)
```
